The Rapid Cycleway Prioritisation Tool

### 2020-06-15 rapid-slides.Rmd
Add results for regions
Complete slides

# How can I find the results for my area?

@@

@@

# Case study: Leeds

@@

## What are the key limitations of the tool?

@@

@@

## How to cope with reduced public transport capacity post COVID-19?

# Data

# Methods

# Results

# Demo

# Links I

- Sheffield [infrastructure](https://www.cyclesheffield.org.uk/2018/01/01/cyclesheffield-response-to-portobello-trippet-lane-cycle-route-designs/)

- Article on Yorkshire Voice on the Leeds-Bradford [Cycle Superhighway](http://www.yorkshire-voice.com/mixed-views-as-29m-cycle-superhighway-linking-leeds-and-bradford-nears-completion/)

- A detailed article on the same cycleway by [Mark Strong](https://aseasyasridingabike.wordpress.com/2016/08/11/a-visit-to-the-leeds-bradford-cycle-superhighway/)

@@

# Links II

@@

- Maps of roads with 'spare lanes' in 10 cities from our our 'cyipt' [website](https://www.cyclinguk.org/article/10-cities-where-pop-bike-lanes-could-benefit-millions-explore-maps)

@@

# Limitations and next steps

- Source: Adam Reynolds on a [GitHub issue](https://github.com/luukvdmeer/sfnetworks/issues/13)

@@

- www.cyipt.bike

- Pop-up cycleway info: watch this space

```{r, echo=FALSE, eval=FALSE}
# export code from slides
knitr::purl("tds-regional-street.Rmd")
```

>>>>

### How can I find the results for my area?

Head to [cyipt.bike/rapid/](https://www.cyipt.bike/rapid/)

![](https://raw.githubusercontent.com/cyipt/popupCycleways/master/figures/results-regions.png)
]

@@

- Aim: to support evidence-based prioritisation of bids for Tranche 2 of the Emergency Active Travel Fund
- Complementing local knowledge and stakeholder engagement
- Scoping of options
- Order of implementations

Investment should depend on many factors including:

- cycling potential (default metric to rank schemes)
- total length of cycling infrastructure created
- cycling potential multiplied by road section length

@@

# Case study demo: Leeds

@@

## Limitations

- Narrow focus on road space reallocation options
- No economic appraisal
  - Use the Active Mode Appraisal Toolkit ([AMAT](https://www.gov.uk/government/publications/tag-social-and-distributional-impacts-worksheets)) 
- The best locations for new cycleways may not always have space
  - Search for parallel routes, which may be available
- Many options not in top routes
  - see cohesive network and look for other option
- The road network data is from 2017 and widths are estimates
  - Compare with real world knowledge
- Only work and school trips included
  - Use local knowledge of new developments and other 'trip attractors
- Prioritises routes in large cities in authorities with multiple settlements
  - Use alternative sources of information, including the PCT

@@

- See the technical specification [here](https://github.com/cyipt/popupCycleways/releases/download/v1/report.pdf)

Data about the tools informing the model can be found here:

- The [Propensity to Cycle Tool](https://www.pct.bike/)
- The [Cycling Infrastructure Prioritisation Tool](https://www.cyipt.bike)
- [OpenStreetMap](https://www.openstreetmap.org/#map=7/52.486/-2.428&layers=C)

- Code underlying the project can be accessed [here](https://github.com/cyipt/popupCycleways).
- Support the project with technical input via the [GitHub issue tracker](https://github.com/cyipt/popupCycleways/issues/14)
- Data generated by the project can be downloaded from GitHub (e.g. see GeoJSON files for London [here](https://github.com/cyipt/popupCycleways/tree/gh-pages/v1/greater-london)).

@@

# Links

@@

@@

@@

# Next steps

- Many future directions of travel including evidence to support [Low Traffic Neighbourhoods](https://github.com/luukvdmeer/sfnetworks/issues/13)

@@

- www.cyipt.bike/rapid
